---
title: "Set To Origin"
author: "eNVy"
date: "6/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

knitr::opts_knit$set(root.dir = "./")

library(here)
here()
```

```{r}
library(tidyverse)
```

```{r}
df_raw = read_csv(here("Data/UCI_handWritten/data.csv"))

df_raw %>% head()
```


```{r}
df_raw %>% 
  rowwise() %>% 
  transmute(
  
  char = char, 
  key = key, 
  person = person, 
  attemp_num_one = attempt_one %>% 
    str_split(pattern = " # ", simplify = T) %>% 
    str_c(collapse = " ") %>% 
    str_split(" ") %>% 
    map(., as.integer) %>% 
    unlist() %>% list(), 
  
  attemp_num_two = attempt_two %>% 
    str_split(pattern = " # ", simplify = T) %>% 
    str_c(collapse = " ") %>% 
    str_split(" ") %>% 
    map(., as.integer) %>% 
    unlist() %>% list()
  )  %>% 
  transmute(
    
    char = char, 
    key = key, 
    person = person, 
    x1 = list(attemp_num_one[seq(1, length(attemp_num_one), 2)]),
    y1 = list(attemp_num_one[seq(0, length(attemp_num_one), 2)]),
    x2 = list(attemp_num_two[seq(1, length(attemp_num_two), 2)]),
    y2 = list(attemp_num_two[seq(0, length(attemp_num_two), 2)])) -> df
```

# Set all starting points of the data to Origin (0,0)
```{r}
df %>% head()
```
All the elements of the data is set to subtract the first value of the list. So that every starting point for every written object starts at (0,0)

```{r}
df %>%
  rowwise() %>% 
  mutate(
    x1 = list(c(x1 %>% unlist()) - x1[1] ),
    y1 = list(c(y1 %>% unlist()) - y1[1] ),
    x2 = list(c(x2 %>% unlist()) - x2[1] ),
    y2 = list(c(y2 %>% unlist()) - y2[1] )) -> df_origin
```

```{r}
df_origin %>% head()
```

Moving forward only the alphabetical characters will be filtered. 

```{r}
df_origin %>% 
  filter(tolower(char) %in% letters) -> df_origin
```

```{r}
df_origin %>%
  rowwise() %>% 
  mutate(
    len_x = length(x1) 
  ) %>% 
  group_by(char) %>% 
  summarise(mean_length = mean(len_x))

# when ungrouped mean of approx 64 letters
```

Interpolation to provide an even scale of time and events

```{r}
# initail test with single letter
df_origin[3,] %>% 
  rowwise() %>% 
    transmute(
    x1 = x1 %>% unlist() %>% list(), 
    y1 = y1 %>% unlist() %>% list(), 
    new_x1 = (x1 %>% unlist() %>% approx(x = ., n = 30))[[2]] %>% list(),
    new_y1 = (y1 %>% unlist() %>% approx(x = ., n = 30))[[2]] %>% list() 
  ) %>% pull(new_x1)
  
```
Determine the **n** based on some reasoning
For now it will be 100

```{r}
df_origin %>% 
  rowwise() %>% 
  transmute(
    char = char, 
    key = key, 
    person = person, 
    inter_x1 = (x1 %>% unlist() %>% approx(x = ., n = 100))[[2]] %>% list(),
    inter_y1 = (y1 %>% unlist() %>% approx(x = ., n = 100))[[2]] %>% list(),
    inter_x2 = (x2 %>% unlist() %>% approx(x = ., n = 100))[[2]] %>% list(),
    inter_y2 = (y2 %>% unlist() %>% approx(x = ., n = 100))[[2]] %>% list()
  ) -> df_interpolated
```

Test graphs on initial data and new interpolated data


```{r}
ggplot() + 
  geom_point(data = df_interpolated %>% 
              filter(key == 1) %>% 
              unnest(cols = c(inter_x1, inter_y1)), 
            aes(x = inter_x1, y = inter_y1), color = "indianred4") + 
  geom_point(data = df_origin %>% 
              filter(key == 1) %>% 
              unnest(cols = c(x1, y1)), 
            aes(x = x1, y = y1), color = "slateblue4") + 
  scale_y_reverse()

# reds = new_data
# blues = earlier data
```
Looks okay to me !!!

# Concatenated function

```{r}

mostLameFuncEver <- function(n_int = 100) {
# remove head in next line for real use-case 
  
df_raw %>% head() %>% 
  rowwise() %>% 
  transmute(
  
  char = char, 
  key = key, 
  person = person, 
  attemp_num_one = attempt_one %>% 
    str_split(pattern = " # ", simplify = T) %>% 
    str_c(collapse = " ") %>% 
    str_split(" ") %>% 
    map(., as.integer) %>% 
    unlist() %>% list(), 
  
  attemp_num_two = attempt_two %>% 
    str_split(pattern = " # ", simplify = T) %>% 
    str_c(collapse = " ") %>% 
    str_split(" ") %>% 
    map(., as.integer) %>% 
    unlist() %>% list()
  )  %>% 
  
  mutate(
    x1 = list(attemp_num_one[seq(1, length(attemp_num_one), 2)]),
    y1 = list(attemp_num_one[seq(0, length(attemp_num_one), 2)]),
    x2 = list(attemp_num_two[seq(1, length(attemp_num_two), 2)]),
    y2 = list(attemp_num_two[seq(0, length(attemp_num_two), 2)])) %>% 
  
  mutate(
    x1 = list(c(x1 %>% unlist()) - x1[1] ),
    y1 = list(c(y1 %>% unlist()) - y1[1] ),
    x2 = list(c(x2 %>% unlist()) - x2[1] ),
    y2 = list(c(y2 %>% unlist()) - y2[1] )) %>% 
  
  transmute(
    char = char, 
    key = key, 
    person = person, 
    inter_x1 = (x1 %>% unlist() %>% approx(x = ., n = n_int))[[2]] %>% list(),
    inter_y1 = (y1 %>% unlist() %>% approx(x = ., n = n_int))[[2]] %>% list(),
    inter_x2 = (x2 %>% unlist() %>% approx(x = ., n = n_int))[[2]] %>% list(),
    inter_y2 = (y2 %>% unlist() %>% approx(x = ., n = n_int))[[2]] %>% list()
  )
}

mostLameFuncEver()
```


